Anomalous waves triggered by abrupt depth changes: experiments and truncated KdV theory

### 2019-10-11 paper2_JNLS/paper.tex
NM

	In Fig.~\ref{uhist} we show the displacement distributions that were measured in the experiments (top row) versus those that emerge from the TKdV simulations (bottom row). The experimental histograms represent exactly the same data depicted in Fig.~\ref{ExpDiagStats}, only converted to dimensionless displacement, $u$, for comparison against theory. Meanwhile, the TKdV distributions are extracted  from the long-time history of several trajectories sampled from the Gibbs ensemble, i.e.~mixed long-time/ensemble histograms. All histograms are shown on a semi-log scale to facilitate comparison of the tails, where extreme events lie.

>>>>

	In Fig.~\ref{uhist} we show the distributions of surface displacement that were measured in the experiments (top row) versus those that emerge from the TKdV simulations (bottom row). The experimental histograms represent exactly the same data depicted in Fig.~\ref{ExpDiagStats}, only converted to dimensionless displacement, $u$, for comparison against theory. Meanwhile, the TKdV distributions are extracted  from the long-time history of several trajectories sampled from the Gibbs ensemble, i.e.~mixed long-time/ensemble histograms. All histograms are shown on a semi-log scale to facilitate comparison of the tails, where extreme events lie.
